---
title: "Back to School"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Dependency
```{r}
library(tidyverse)
```
### Read CSV file
```{r}
students <-read_csv("../Resources/students.csv")
```
### Preview tibble
```{r}
head(students)
```

### A list of all schools
```{r}
# unique(dataset, variable) displays unique elements from that column
unique(students$school_name)
```

### Calculate the total count of schools
```{r}

# Use length() to identify the number of schools
unique_schools <- unique(students$school_name) 
length(unique_schools)

```

### Calculate the total number of students
```{r}
# nrow() returns the number of rows
student_count <- nrow(students)
#print(student_count)

paste("There are a total of", student_count, "students.")
```

### Calculate the average reading and math scores
```{r}

mean_reading_score <- summarize(students, mean(reading_score))
paste("The average reading score is", mean_reading_score)

mean_math_score <- summarize(students, mean(math_score))
paste("The average math score is", mean_math_score)
```

### Calculate the percentage of students with passing reading scores
### equal to or greater than 70%.
```{r}
passing_reading <- filter(students, reading_score >= 70)
count_passing <- (passing_reading)

total <- nrow(students)

percentage_passing_reading <- count_passing/total * 100

paste(percentage_passing_reading, "% of the students have passing reading scores.")
```

### Calculate the percentage of students with passing math scores,
### equal to or greater than 70%.
```{r}


paste(percentage_passing_math, "% of the students have passing math scores.")
```

### Calculate the percentage of overall passing equal to or greater than 70%.
```{r}
filter(students, math_score )

paste(percentage_passing_overall, "% of the students have passing math and reading scores.")
```

### Calculate the average math and reading scores by school
```{r}
df <- group_by(students, school_name)
summarize(df, avg.reading=mean(reading_score), avg.mean=mean(math_score))

```

### Calculate the average math and reading scores by grade level at each school
```{r}
dfbygrade <- group_by(students, school_name, grade)
summarize(dfbygrade, avg.reading=mean(reading_score), avg.mean=mean(math_score))

```
